### 2016-09-01 padics/hw1.tex
pushy push

\item Suppose that $F$ is a finite field and $x\in F\setminus\{0\}$. Prove that there exists $n\in\NN$ such that $x^{n}=1$.
\end{enumerate}
\end{document}

>>>>

\item Suppose that $F$ is a finite field and $x\in F\setminus\{0\}$. Prove that there exists $n\in\NN$ such that $x^{n}=1$.
\begin{quote}
\textit{\textbf{Proof:}} Consider $x^{r}=x^{s}$ for $s\neq r\in\NN$ where $s>r$ without loss of generality. We know that for every element in $F$, there is a multiplicative inverse of that element, so we define $(x^{r})^{-1}=x^{-r}$. Then $x^{-r}x^{r}=x^{-r}x^{s}$ and $1=x^{s-r}$. Since $s>r$, $s-r\in\NN$, so we have found the $n$ we were looking for.
\end{quote}
\end{enumerate}
\end{document}
